### 2015-06-26 narrative/intro.tex
adding missing files and editing the intro

Exascale scientific discovery will be severely bottlenecked without
sufficient new research into managing and storing the large amounts of data
that will be produced during the simulation, and analyzed for months
afterwards.  
%
In this project we will demonstrate novel techniques to
facilitate efficient mapping of data objects, even partitioning individual
variables, from the user space onto multiple storage tiers, and enable
application-guided data reductions/transformations to address capacity and
bandwidth bottlenecks, while constraining the error to be within user
provided bounds.
%
We will address the associated I/O and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into critical
scientific processes, demonstrating the validity of our approach in key DOE
domains.

>>>>

Exascale scientific discovery will be severely bottlenecked without
sufficient new research into managing and storing the large amounts of data
that will be produced during the simulation, and analyzed for months
afterwards.  
%
In this project we will demonstrate novel techniques to
facilitate efficient mapping of data objects, even partitioning individual
variables, from the user space onto multiple storage tiers, and enable
application-guided data reductions/transformations to address capacity and
bandwidth bottlenecks, while constraining the error to be within user
provided bounds. 
%
We will address the associated I/O and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into critical
scientific processes, demonstrating the validity of our approach in key DOE
domains.  Our techniques will be to research novel techniques into a Scalable 
Storage Software Infrastructure by integrating services from the middle-ware layer which will
talk to the applications, with the Storage system. The negotation between these layers will
be a fundamental service which we will create in this project to ensure that users will be able
to save `'the best'' amount of data in the different storage tiers.
